%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Definimos una seccin para la bibliografa
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{1} 

\bibitem{Anderson2008} Anderson, J., S. Baggett, P. Jeffrey, L. McPherson, J. Marks and E. Rosenblum (2008). {\em Public acceptance of water reuse. Water reuse: An international survey of current practice}. Blanca, J. and Asano, T. (eds.), IWA Publishing London, UK.

\bibitem{Anderson2007} Anderson, P. (2007). {\em Water reuse: An integral part of sustainable water resource planning}. Illinois Institute of Technology.

\bibitem{Arkin1968} Arkin, H. and R. R. Colton (1968). {\em Tables for statisticians}. Barnes and Noble, New York, NY (EUA).

\bibitem{Asano2007} Asano, T., F. L. Burton, H. L. Leverenz, R. Tsuchihashi and G. Tchobanoglous (2007). {\em Water Reuse, Issues, Technologies, and Applications}. McGraw-Hill United States of America.

\bibitem{Bell2008} Bell, S. and V. Aitken (2008). {\em The Socio-technology of Indirect Potable Water Reuse}. Water Science and Technology: Water Supply. 8, 441-448.

\bibitem{CONAPO2008} CONAPO, C. N. d. P. (2008). {\em Proyecciones de la poblacin de Mxico, de las entidades federativas, de los municipios y de las localidades}. CONAPO Hamburgo 135, Col. Jurez, Mxico, D. F. 

\bibitem{Hartley 2003} Hartley, T. W. (2003). {\em Water Reuse: Understanding Public Perception and Participation}. IWA Publishing, Washington DC, USA.

\bibitem{Mendoza2005} Mendoza-Espinosa, L. G. and R. d. J. Ramrez-Acosta (2005). {\em Economa del agua en Baja California, Reuso de aguas residuales tratadas bajo mecanismos de mercado}. 1 ed., Universidad Autnoma de Baja California, Mexicali, Baja California.

\bibitem{Sierra2006} Sierra, C. F. M. (2008). {\em Lnea Morada}. CESPT Tijuana, Baja California.

\bibitem{SPSS2006} SPSS (2006). {\em Manual del usuario de SPSS Base 15.0}. SPSS Inc., Chicago, IL.

\end{thebibliography} 